Verifying Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
Simplify and chang example in 'Region declarations and variables''

Region specifications can be assigned to region variables via
a region declaration, which can be used later in another
specification. For example, the last specification
 example above can be restated as:
%%
\begin{minted}{fortran}
!= region :: r1 = forward(depth=1, dim=1)
!= region :: r2 = forward(depth=1, dim=2)
!= region :: robertsCross = r1*r2
!= stencil robertsCross :: a
\end{minted}
This is especially useful for common stencil patterns, such as Roberts cross,
as the region can be defined once and reused.
%%
\paragraph{Modifiers}
%%
Region specifications can be modified
by \emph{approximation} and \emph{multiplicity} information
(in \textit{spec} in Fig.~\ref{fig:syntax}).

>>>>

Region specifications can be assigned to region variables via
region declarations. For example, the last specification
 example above can be restated as:
%%
\begin{minted}{fortran}
!= region :: r1 = centered(depth=1, dim=1) * pointed(dim=2)
!= region :: r2 = centered(depth=1, dim=2) * pointed(dim=1)
!= region :: fivePoint = r1 + r2
!= stencil fivePoint :: a
\end{minted}
This is especially useful for common stencil patterns, such as five point
stencil, as the region can be defined once and reused many times later.
%%
\paragraph{Modifiers}
%%
Region specifications can be modified
by \emph{approximation} and \emph{multiplicity} information
(in \textit{spec} in Fig.~\ref{fig:syntax}).
